\cvsection{International Experience}

\begin{cventries}
  {\fontsize{8.8pt}{1.15em}\selectfont
  \cventry
    {\textit{Global Connect Fellow}}
    {Nanyang Technological University}
    {Singapore}
    {Feb. 2026 -- Mar. 2026}
    {
      \begin{cvitems}
        \item {\textbf{Program:} NTU Global Connect Fellowship}
        \item {Selected as 1 of 39 young scholars worldwide and 1 of 5 outstanding Vietnamese young scholars funded fully for the Global Connect Fellowship program at NTU, Singapore ($\sim$2\% acceptance rate from $\sim$2,700 applicants).}
      \end{cvitems}
    }

  \cventry
    {\textit{Exchange Student}}
    {National University of Singapore}
    {Singapore}
    {Aug. 2025 -- Dec. 2025}
    {
      \begin{cvitems}
        \item {\textbf{Program:} DiscoverNUS}
        \item {Selected as one of 8 outstanding VNU students receiving a fully funded scholarship DiscoverNUS \& the NUS ASEAN Master’s Scholarship Programme.}
        % \item {Completed a one-semester academic exchange, gaining broader exposure to engineering education, international research culture, and interdisciplinary learning.}
      \end{cvitems}
    }

  \cventry
    {\textit{Research Intern}}
    {National Chung Cheng University}
    {Taiwan}
    {May. 2025 -- Jul. 2025}
    {
      \begin{cvitems}
        \item {\textbf{Program:} Taiwan Experience Education Program (TEEP)}
        \item{Selected as one of 28 global students to intern at AIM-HI, CCU funded by Ministry of Education, Taiwan}
        % \item {Worked at Advanced Institute of Manufacturing with High-tech Innovations (AIM-HI) -- one of leading tech institutions in Taiwan, participating in smart sensing manufacturing research project.}
      \end{cvitems}
    }

  \cventry
    {\textit{VNU representative}}
    {Universitas Gadjah Mada \& Kyushu University}
    {Indonesia}
    {Feb. 2025}
    {
      \begin{cvitems}
        \item {\textbf{Program:} ASEAN in Today's World}
        \item {Selected as one of four excellent VNU representatives to participate the program funded by Kyushu University, Japan.}
        % \item {Participated in an ASEAN-focused academic program, strengthening regional understanding, cross-cultural communication, and awareness of science, technology, and society in Southeast Asia.}
      \end{cvitems}
    }

  \cventry
    {\textit{VNU Representative}}
    {Ngee Ann Polytechnic}
    {Singapore}
    {Feb. 2024}
    {
      \begin{cvitems}
        \item {\textbf{Program:} Temasek Foundation Specialist's Community Action \& Leadership Exchange}
        \item {Selected as one of 29 VNU students to receive a fully-funded scholarship for the program by Temasek Foundation.}
        % \item {Contributed to a group project on youth leadership and sustainability in urban development in Vietnam and Singapore.}
        % \item {Engaged in a regional leadership and community action program, developing teamwork, communication, and social responsibility in an international environment.}
      \end{cvitems}
    }

    % \cventry
    % {\textit{VNUIS Representative}}
    % {Overseas Immersion Programme}
    % {Vietnam}
    % {Feb. 2023}
    % {
    %   \begin{cvitems}
    %     \item {Engaged in an international immersion program with students from Ngee Ann Polytechnic, Singapore, developing cross-cultural communication, teamwork, and exposure to applied learning in a regional context.}
    %   \end{cvitems}
    % }
  }
\end{cventries}