\cvsection{Projects}
\begin{cventries}

  \cventry
    {\textit{Leader}}
    {Adaptive Control for AUV with Wireless Power Transfer System \text{(Graduation Thesis)}}
    {Vietnam}
    {Apr. 2026 -- Present}
    {
      \begin{cvitems}
        \item {Developing an AUV prototype that integrates motion control with wireless charging requirements.}
        \item {Focusing on station keeping and stable positioning during planar wireless power transfer.}
        % \item {Designing the system as a foundation for future work on robust control and docking-free underwater charging.}
      \end{cvitems}
    }

  \cventry
    {\textit{Leader}}
    {Advanced 3D Wireless Power Transfer System for AUVs}
    {Singapore}
    {Feb. 2026 -- Mar. 2026}
    {
      \begin{cvitems}
        \item {Studied relay-coil-enhanced spatial wireless power transfer systems for autonomous underwater vehicle charging.}
        \item {Analyzed coil configurations, equivalent circuit behavior, power transfer efficiency, and load-dependent system performance.}
        % \item {Explored system-level integration for docking-free underwater charging of intelligent underwater devices.}
        \item {Got Most Popular Poster Award in NTU GCF Final Research Presentation}
      \end{cvitems}
    }

  \cventry
    {\textit{Leader}}
    {Prediction of Cutting Force and Tool Wear Using Machine Learning Methods}
    {Taiwan/Remote}
    {May. 2025 -- Present}
    {
      \begin{cvitems}
        \item {Applying machine learning models (Random Forest, XGBoost, and Support Vector Regression) to Taguchi machining datasét.}
        \item {Built data-driven models for cutting force and tool wear prediction in CNC milling using experimental machining datasets.}
        % \item {Explored the gap between model prediction and real machining signals under noisy and limited experimental conditions.}
      \end{cvitems}
    }

  \cventry
    {\textit{Member}}
    {Adaptive Fuzzy Logic in Backstepping Control for 3-DOF Parallel Delta Robot}
    {Vietnam}
    {Oct. 2023 -- Jul. 2024}
    {
      \begin{cvitems}
        \item {Designed and built a 3-DOF delta parallel robot prototype for motion control research.}
        \item {Implemented adaptive fuzzy backstepping control to improve trajectory tracking under uncertainties.}
        \item {Presented in International Conference on Advances in Information and Communication Technology 2024.}
        % \item {Validated the control approach through mathematical modeling and MATLAB simulation.}
      \end{cvitems}
    }

  \cventry
    {\textit{Member}}
    {Prediction of Personal Protective Equipment Using YOLOv5s}
    {Vietnam}
    {Jan. 2023 -- Jul. 2023}
    {
      \begin{cvitems}
        % \item {Prepared a construction-site image dataset for detecting personal protective equipment categories.}
        \item {Trained YOLOv5s-based object detection models and compared  six activation functions for performance improvement.}
        \item {Evaluated model performance using precision, recall, mAP@0.5, and mAP@0.5--0.95.}
        \item {Presented in National Conference on Smart Technology Application in Industry 4.0, Smart City, and Sustainability 2023.}
      \end{cvitems}
    }

  % \cventry
  %   {\textit{Leader}}
  %   {iRoom -- Smart Occupancy Tracking System}
  %   {Vietnam}
  %   {Dec. 2022}
  %   {
  %     \begin{cvitems}
  %       \item {Developed a privacy-preserving IoT occupancy tracking prototype using dual IR-sensor directional logic to estimate room occupancy without camera-based monitoring.}
  %       \item {Integrated an ESP32-C3, DHT11 environmental sensing, local status display, and Firebase Realtime Database for real-time monitoring of occupancy, temperature, humidity, and room status.}
  %       \item {Received the Spirit Prize at IEEE SEACAS Hackathon 2022.}
  %     \end{cvitems}
  %   }

\end{cventries}
