\cvsection{Research Experience}

\begin{cventries}

  \cventry
    {Research Fellow}
    {Water \& Energy Research Lab, School of EEE, Nanyang Technological University}
    {Singapore}
    {Feb. 2026 -- Present}
    {
      \begin{cvitems}
        \item {Project: Advanced 3D Wireless Power Transfer System for Autonomous Underwater Vehicles.}
        \item {Investigating relay-coil-enhanced spatial wireless power transfer for AUV charging, with emphasis on power transfer efficiency, coil configuration, and system-level integration.}
        \item {Optimizing the mechanical design of AUVs to support underwater operation, wireless charging integration, and long-endurance autonomy.}
        \item {Exploring underwater communication between the transmitter and receiver sides of the system for reliable AUV charging coordination.}
      \end{cvitems}
    }

  \cventry
    {Research Intern}
    {AISC Lab, AIM-HI Institute, National Chung Cheng University}
    {Chiayi, Taiwan}
    {May 2025 -- Jul. 2025}
    {
      \begin{cvitems}
        \item {Project: Smart Sensing Technology for Smart Manufacturing.}
        \item {Developed a data-driven approach to estimate dynamic cutting forces in milling using 12 large-scale datasets.}
        \item {Combined nonlinear system analysis with sparse identification methods to model and predict cutting force behavior.}
        \item {Achieved moderate prediction accuracy with $R^2$ between 0.5 and 0.6 compared with ground-truth measurements.}
      \end{cvitems}
    }

  \cventry
    {Remote Research Student}
    {AISC Lab, AIM-HI Institute, National Chung Cheng University}
    {Remote}
    {Aug. 2025 -- Present}
    {
      \begin{cvitems}
        \item {Project: Prediction of cutting force model using AI and data-driven methods.}
        \item {Implementing machine learning models, including Random Forest and XGBoost, using 27 large-scale datasets collected through a Taguchi-designed experiment.}
        \item {Developing data-driven modeling pipelines for feature engineering, model training, and cutting force prediction in machining processes.}
      \end{cvitems}
    }

  \cventry
    {Student Researcher}
    {Intelligent Control and Artificial Intelligence Laboratory, VNUIS}
    {Hanoi, Vietnam}
    {Sep. 2022 -- Present}
    {
      \begin{cvitems}
        \item {Project: Adaptive Fuzzy Logic in Backstepping Control for 3-DOF Parallel Robot.}
        \item {Designed the mechanical model and physical prototype of a 3-DOF delta robot, and implemented adaptive fuzzy backstepping control for robust trajectory tracking under uncertainties.}
        \item {Reduced joint trajectory deviations to less than 0.15 rad, with stability reached in 0.15--0.2 s in simulation studies.}
        \item {Project: Detection of Personal Protective Equipment in Construction Sites.}
        \item {Built a dataset of 2,632 construction-site images across five classes and trained YOLOv5s with multiple activation functions for PPE detection.}
      \end{cvitems}
    }

\end{cventries}