\cvsection{Selected Working Experience}

\begin{cventries}
  \cventry
    {\textit{Engineering Intern}}
    {ETEK Automation Solutions JSC}
    {Hanoi, Vietnam}
    {Mar. 2025 -- May 2025}
    {
      \begin{cvitems}
        \item {\textbf{Project:} AGV Virtual Simulation for Automated Warehouse Logistics -- VINFAST Hai Phong.}
        \begin{itemize}
          \item {Sketched AGV/AMR traffic intersections using AutoCAD and simulated warehouse logistics operations using Visual Components Premium 4.6.}
          \item {Monitored AGV/AMR behavior, identified simulation errors, and supported troubleshooting of automated logistics workflows.}
        \end{itemize}
      \end{cvitems}
    }

  \cventry
    {\textit{Collaborator}}
    {Vietnam E-Commerce and Digital Economy Agency, Ministry of Industry and Trade}
    {Hanoi, Vietnam}
    {Jul. 2023 -- Sep. 2023}
    {
      \begin{cvitems}
        \item {\textbf{Project:} Consultancy Support and Sales Policy Development for E-Commerce Website.}
        \begin{itemize}[leftmargin=1.8em, itemsep=0pt, topsep=0.1em, parsep=0pt]
          \item{Coordinated with SMEs across Dak Nong and An Giang provinces to support e-commerce platform development.}
          \item{Assisted in website design, content management, and preparation of technical manual documents.}
        \end{itemize}
      \end{cvitems}
    }
    
  % \cventry
  %   {\textit{Teaching Collaborator}}
  %   {Hung STEM Robotics Lab}
  %   {Hanoi, Vietnam}
  %   {Jul. 2022 -- Dec. 2022}
  %   {
  %     \begin{cvitems}
  %       \item {Mentored students for the World Robot Olympiad 2022 Vietnam and supported the development of LEGO-based robotics modules.}
  %       \item {Delivered hands-on STEM robotics sessions using LEGO NXT for students at Grammar Newton International Bilingual School, Hanoi.}
  %     \end{cvitems}
  %   }
\end{cventries}
