%-------------------------
% Resume in Latex
% Author : Shubhi Rani
% License : MIT
%------------------------

\documentclass[letterpaper,9pt]{extarticle}

% \documentclass[letterpaper,10.8pt]{article}
	
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}
\usepackage{graphicx}

%for social icons
\usepackage{fontawesome5}
\usepackage{academicons}
\usepackage{quotes}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1in}

\urlstyle{rm}
%tabularx environment
\usepackage{tabularx}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-3pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeItemWithoutTitle}[1]{
  \item\small{
    {\vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}


\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}
%----------HEADING-----------------

\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{{\LARGE Khac-Long Nguyen}} & \href{mailto:nk.long723@gmail.com}{\raisebox{-0.05\height}\faEnvelope \ nk.long723@gmail.com}\\
  \href{https://www.linkedin.com/in/longnk0702/}{\raisebox{-0.05\height}\faLinkedin\ Long Nguyen Khac} & \href{https://join.skype.com/invite/}{\raisebox{-0.05\height}\faMobile \ (+84)358036759} \\
  \href{https://longnk0702.github.io/}{\raisebox{-0.05\height}\faGithub\ LongNk0702}
\end{tabular*}

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {International School, Vietnam National University, Hanoi (VNUIS)}{Hanoi, Vietnam}
      {BEng. Automation and Informatics}{08/2021 -  07/2026}
        \begin{itemize}
            \item QS WUR Ranking 386 for Engineering and Technology \href{https://www.topuniversities.com/universities/vietnam-national-university-hanoi}{(Source)}
            \item GPA: 3.71/4.0 (Rank \#3 of the Cohort)
            \item Transcripts: \href{https://www.dropbox.com/scl/fi/g45n25qu44qbhe5643vi6/Khac-Long-Nguyen-Academic-Transcript.pdf?rlkey=sckmcezviyhpbe7qkt35zz9cp\&st=c8nqbfm9\&dl=0}{Click here}
        \end{itemize}
    \resumeSubheading
    {National University of Singapore (NUS)}{Singapore}
    {Exchange Semester I, AY25/26}{08/2025 - 12/2025}
    \begin{itemize}
        \item QS WUR Ranking 12 for Engineering and Technology (\href{https://www.topuniversities.com/universities/national-university-singapore-nus}{Source})
        \item Courseworks: Robot Mechanics and Control (ME4245), Electric Drives and Control (EE4502), Calculus (MA2002).
    \end{itemize}
  \resumeSubHeadingListEnd
%-----------WORK EXPERIENCE-----------------
\section{Research Experience}
  \resumeSubHeadingListStart
%Research Intern, CCU
    \resumeSubheading
    {AIM-HI Institute, National Chung Cheng University}{Chiayi, Taiwan}
    {Research Intern}{05/2025 -  07/2025}
    \begin{itemize}
        \item \textbf{Project:} Smart Sensing Technology for Smart Manufacturing. 
        \begin{itemize}
            \item Developed a data-driven approach to estimate dynamic cutting force model in milling process by combining nonlinear system analysis with qualitative simulation.
            \item Processed and trained 12 datasets of the cutting forces, each containing multi-channel sensor signals (three-axis dynamometer, spindle speed, feed rate, and depth of cut).
            \item Implemented visualization and error analysis of predicted vs. actual measured cutting forces using Python.
            \item Results: Prediction accuracy of 60-70\% compared to experimental ground-truth cutting force measurements.
            \item \textbf{Supervisor:} \href{https://deptime.ccu.edu.tw/p/405-1102-22906,c2239.php?Lang=en}{Prof. Her-Terng Yau}
        \end{itemize}
        \vspace{-0.55cm}
    \end{itemize}
%Remote Research, CCU
    \resumeSubheading
    {}{}
    {Remote Research}{08/2025-Current}
    \begin{itemize}
        \item \textbf{Project: } Prediction of cutting force model using AI and data-driven methods
        \begin{itemize}
            \item Implementing 03 machine learning models and 01 data-driven model to predict cutting force.
            \item Training 27 experienced datasets collected by Taguchi method.
            \item \textbf{Supervisor:} \href{https://deptime.ccu.edu.tw/p/405-1102-22906,c2239.php?Lang=en}{Prof. Her-Terng Yau}
        \end{itemize}
    \end{itemize}
%IC&AI Lab
    \resumeSubheading
    {Intelligent Control and Artificial Intelligence Lab, VNUIS}{Hanoi, Vietnam}
    {Student Research}{09/2022 - Current}
    \begin{itemize}
        \item \textbf{Project:} Implementation Model Predictive Control for Machining System (Current)
            \begin{itemize}
                \item Reviewing more than 30 papers in control of machining system and cutting force prediction.
                \item Combining machine learning and MPC model to control machining system.
                \item \textbf{Supervisor:} \href{https://www.is.vnu.edu.vn/en/assoc-prof-phd-nguyen-nhu-tung/}{Assoc. Prof. Nguyen Nhu Tung}
            \end{itemize}
        \item \textbf{Project:} Implementation Adaptive Control for 3-DOF Parallel Robot (2024)
            \begin{itemize}
                \item Designed mechanical model and physical prototype of 3-DOF delta parallel robot.
                \item Applied adaptive fuzzy logic combined with backstepping control for robust trajectory tracking under uncertainties.
                \item Simulation Results (Matlab/Simulink):
                    \begin{itemize}
                        \item Reduced steady-state deviation at J2 from 1.2 rad (Backstepping) to nearly 0 rad (Backstepping + Fuzzy). 
                         \item Settling time improved from 0.3 s to 0.15–0.2 s.
                         \item Coordinate tracking (\(x, y, z\)) stabilized with maximum deviation 0.35 rad.
                    \end{itemize}
                \item Results: Published in Lecture Notes in Networks and Systems, Springer, Q4.
                \item \textbf{Supervisor:} \href{https://www.is.vnu.edu.vn/en/phd-le-xuan-hai/}{Dr. Le Xuan Hai}
            \end{itemize}
        \item \textbf{Project:} Detection of Personal Protective Equipment (PPE) in Construction Sites (2023)
            \begin{itemize}
                \item Built a custom dataset of 2,632 real construction site images across 5 PPE classes (helmet, vest, gloves, boots, person)
                \item Trained and evaluated YOLOv5s with 6 activation functions, SiLU achieved the best performance.
                \item Results: Precision 84.8\%, Recall 80.2\%, mAP@0.5 83.9\%, mAP@0.5--0.95 43.6\%. 
                \item \textbf{Supervisor:} \href{https://www.is.vnu.edu.vn/en/phd-kim-dinh-thai/}{Dr. Kim Dinh Thai}
            \end{itemize}
    \end{itemize}
\resumeSubHeadingListEnd

%-----------Teaching EXPERIENCE-----------------
\section{Teaching Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
    {Faculty of Engineering and Technology, VNUIS}{Hanoi, Vietnam}
    {Teaching Assistant}{09/2023 - 12/2024}
    \begin{itemize}
    %Modeling and Simulation of control system
        \item Modeling and Simulation of Control Systems (Semester 1, AY24/25)
        \begin{itemize}
            \item Assisted in teaching undergraduate course focused on modeling, analysis, and simulation of dynamic systems.
            \item Supported lecturer in preparing tutorials, lab manuals, and course materials.
            \item Mentored student groups on applying simulation tools for robotics, mechatronics and process control applications by using MATLAB/Simulink.
            \item \textbf{Supervisor:} \href{https://www.is.vnu.edu.vn/en/phd-le-xuan-hai/}{Dr. Le Xuan Hai}
        \end{itemize}
    %PLC Programming
        \item PLC Programming (Semester 1, AY24/25)
        \begin{itemize}
            \item Assisted in preparing technical manual documents in Siemens S7-1200 and TIA Portal.
            \item Mentored 01 team programming 4-floor elevator control logic project and 01 team programming pneumatic valve and signal control project.
            \item Assisted with troubleshooting, hardware interfacing, and simulation.
            \item \textbf{Supervisor:} \href{https://www.is.vnu.edu.vn/en/ms-pham-hai-yen/}{MSc. Pham Hai Yen}
        \end{itemize}
    %Microprocessors and microcontrollers
        \item Microprocessors and Microcontrollers (Semester 1, AY23/24)
        \begin{itemize}
            \item Assisted in teaching undergraduate course covering embedded C, and microcontroller interfacing (Arduino, STM32).
            \item Mentored students on debugging techniques using Keil uVision, Arduino IDE, and STM32CubeIDE.
            \item Supported lecturer in preparing tutorials, lab manuals, and course materials.
            \item \textbf{Supervisor:} \href{https://www.is.vnu.edu.vn/en/phd-le-xuan-hai/}{Dr. Le Xuan Hai}
        \end{itemize}
    \end{itemize}
    \resumeSubheading
    {Hung STEM Robotics Lab}{Hanoi, Vietnam}
    {Collaborator}{07/2022 - 12/2022}
    \begin{itemize}
        \item \textbf{Project}: World Robotics Olympiad 2022 Vietnam
        \begin{itemize}
            \item Mentored in a team to participate in World Robotics Olympiad 2022 Vietnam, assisted the team in building up new LEGO modules.
            \item Engaged in teaching STEM robotics classes using LEGO NXT in STEM club at Grammar Newton International Bilingual School, Hanoi.
            \item \textbf{Supervisor:} Mr. Nguyen Quoc Hung (\href{mailto: }{\raisebox{-0.05\height}Email})
        \end{itemize}
    \end{itemize}
\resumeSubHeadingListEnd

%-----------Working EXPERIENCE-----------------
\section{Working Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
    {ETEK Automation Solutions JSC}{Hanoi, Vietnam}
    {Intern}{03/2025 -  05/2025}
    \begin{itemize}
        \item \textbf{Project:} AGV-based Virtual Simulation for Automated Warehouse Logistics – VINFAST Hai Phong.
        \begin{itemize}
            \item Sketched AGV/AMR traffic intersections using AutoCAD and simulated their operations using Visual Components Premium 4.6.
            \item Monitored and analyzed AGV/AMR behavior, identified errors, and troubleshooting.
            \item \textbf{Supervisor:} Mr. Nguyen Ngoc Khanh (\href{mailto:khanh.nn@etek.com.vn}{\raisebox{-0.05\height}Email})
        \end{itemize}

    \end{itemize}
    \resumeSubheading
    {Vietnam E-Commerce and Digital Economy Agency, Ministry of Industry and Trade}{Hanoi, Vietnam}
    {Collaborator}{07/2023 -  09/2023}
    \begin{itemize}
        \item \textbf{Project:} Program for Consultancy Support and Sales Policy Development for E-Commerce Website (CPAPER)
        \begin{itemize}
            \item Coordinated with SMEs across Dak Nong and An Giang province to develop e-commerce platforms.
            \item Assisted in website design, content management, and prepared technical mannual documents.
        \end{itemize}
        
    \end{itemize}
\resumeSubHeadingListEnd

%--------PUBLICATIN------------
\section{Publication}
    \begin{enumerate}
        \item \textbf{Long Nguyen Khac}. et al. \textit{Adaptive Fuzzy Logic in Backstepping Control for 3-DOF Parallel Robot}. International Conference on Advances in Information and Communication Technology, doi: \href{https://doi.org/10.1007/978-3-031-80943-9_57}{10.1007/978-3-031-80943-9\_57}.
        \begin{itemize}
            \item \textit{\underline{Main highlights:} an adaptive fuzzy logic control system integrated with backstepping control for a 3-DOF delta robot.}
        \end{itemize}
        \item \textbf{Long Nguyen Khac}. et al. \textit{YOLOv5s Model with Applied Activation Functions for Personal Protective Equipment Detection in Construction Sites}. Proceedings of National Conference on Smart Technology Applications in Industry 4.0 Smart City, and Sustainability. (2023)
        \begin{itemize}
            \item \textit{\underline{Main highlights:} a deep learning-based approach using YOLOv5s with 06 activation functions with a new dataset of 2632 images for detecting PPE.}
        \end{itemize}
    \end{enumerate}
%-----------TALKS-----------------
\section{Talks}
\begin{tabularx}{\linewidth}{ @{}l r@{} }
\textbf{The 3rd International Conference ICTA 2024} & \hfill Phu Tho, Vietnam \\[3.75pt]
Mechatronics and Automation & \hfill \textit{11/2024} \\[3.75pt]
\multicolumn{2}{@{}X@{}}{}
\vspace{-0.6cm}
\end{tabularx}

%-----------Awards-----------------
\section{Honors and Awards}
\begin{itemize}
\item Selected as one of 20 VNU students received \textbf{DiscoverNUS \& NUS ASEAN Master's Scholarship} for one semester exchange fully funded by National University of Singapore. (Semester 1, AY25/26)
\item Selected as one of 28 global students received \textbf{Taiwan Experience Education Program (TEEP) Scholarship} fully-funded by Ministry of Education, Republic of China (Taiwan) to intern at National Chung Cheng University (CCU).
\item Selected as one of 04 VNU students to participate in \textbf{ASEAN in Today's World} in Indonesia funded by Kyushu Univeristy, Japan.(2025)
\item Selected as one of 20 undergraduate and graduate students received \textbf{TOSHIBA scholarship}. (AY 24/25)
\item Received \textbf{Academic Encouragement Scholarship}, 4/6 semesters.(Semester 1, AY22/23, Semester 1, AY 23/24, Semester 1,2 AY 24/25)
\item Selected as one of 20 VNU students to participate in \textbf{Temasek Foundation Specialist's Community Action \& Leadership Exchange Program} in Singapore fully funded by Temasek Foundation. (2024)
\item Received \textbf{Outstanding Young Face} Award, VNUIS. (2024)
\item Received \textbf{Student with Five Good Merits} Award, VNU. (2024)
\item Received \textbf{Fighting Spirit Prize} in South-East Asia Circuit and System Society Hackathon. (2022)
\end{itemize}
%-------------------------------------------
% Volunteer work  exper ience %
%-----------Awards-----------------
% \section{Volunteer activities}
% \begin{description}[font=$\bullet$]
% \item Volunteered in The 31st Southeast Asian Games (SEA Games). (2022)
% \item Volunteered in Highland Volunteer Program "Tron" in Cao Bang province, VNUIS. (2022)
% \item Blood donated in National Institute of Hematology and Blood Transfusion. (2023, 2024)
% \end{description}


%--------PROGRAMMING SKILLS------------
\section{Skills}
	\resumeSubHeadingListStart
	\resumeSubItem{General skills}{Mathematical modeling, control systems designing, embedded programming, mechanical designing}
	\resumeSubItem{Programming Skills}{Matlab, Python, Embedded C/C++}
    \resumeSubItem{Specialisation} {Adaptive Control, Machine Learning, Robotics}
    % Data Science
    \resumeSubItem{Softwares and Frameworks} {Matlab/Simulink, Solidworks, PyTorch}
    \resumeSubItem{Languages} {Vietnamese (Native), English (IELTS 6.5: Writing 7.0), Chinese (Beginner)}
\resumeSubHeadingListEnd

%--------Reference------------
\section{References}
          
\begin{itemize}[leftmargin=0.35cm]
    \item \textbf{Prof. Her-Terng Yau} \\ 
          Director of AIM-HI, National Chung Cheng University, Taiwan \\
          Email: \href{mailto:yauherterng@gmail.com}{yauherterng@gmail.com}
    \item \textbf{Assoc. Prof. Nguyen Nhu Tung} \\ 
          Senior Lecturer, Faculty of Engineering and Technology \\
          Academic Advisor of Industrial Systems Engineering and Logistics Major \\
          Email: \href{mailto:tungnn@vnu.edu.vn}{tungnn@vnu.edu.vn}

    \item \textbf{Dr. Le Xuan Hai}  \\
          Academic Advisor of Automation and Informatics Major \\
          Director, Intelligent Control and Artificial Intelligence Lab (ICL) \\
          Vice Dean, Faculty of Engineering and Technology, International School, VNU \\
          Email: \href{mailto:hailx@vnu.edu.vn}{hailx@vnu.edu.vn}
\end{itemize}
\end{document}